---
params:
  preset_variables: FALSE
  country_name_: NULL
  path_to_data: NULL
  truncate_contacts_n: NULL
  matrix_boots_n: NULL
output:
  html_document: default
---

<style>
    body .main-container {
        width: 775px;
    }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE )

message(paste("params$country_name_:", params$country_name_))
# Loads libraries and data
library(here)
here::here()

# Read params, if set (no aftion if not)
if (!is.null(params$preset_variables)) {
  preset_variables <- params$preset_variables
}
if (!is.null(params$country_name_)) country_name_ <- params$country_name_
if (!is.null(params$path_to_data)) path_to_data <- params$path_to_data
if (!is.null(params$truncate_contacts_n)) {
  truncate_contacts_n <- params$truncate_contacts_n
}
if (!is.null(params$matrix_boots_n)) matrix_boots_n <- params$matrix_boots_n

source(file.path(here::here(), "r", "setup_report.R"))

```

# CoMix social contact survey: Report for `r country_name_` waves 1-`r max(part$wave)`

*Amy Gimma, Kerry Wong, Kevin Van Zandvoort, CMMID COVID-19 Working Group, Christopher Jarvis, John Edmunds*
London school of Hygiene and Tropical Medicine.

Created as part of the EpiPose project, funded by the EU Horizon 2020 Research and Innovations Programme - project EpiPose (Epidemic Intelligence to Minimize COVID-19’s Public Health, Societal and Economical Impact, No 101003688).

<strong>Report created:</strong> `r format(Sys.time(), '%d %B %Y')` <br>
<strong>Survey dates:</strong> `r format(min(part$survey_date), '%d %B %Y')` to `r format(max(part$survey_date), '%d %B %Y')`


### Introduction & Methods

<br/>

CoMix is a behavioural survey, first launched on 24th of March 2020 in the UK, and launched in `r country_name_` on `r format(min(part$survey_date), "%d of %B %Y")`. The sample is broadly representative of the adult population in `r country_name_`. Participant’s are invited to respond to the survey approximately once every two weeks. In two waves, parents will complete the survey on behalf of a child in their household (17 years old or younger). Participants record direct, face-to-face contacts made on the previous day, specifying certain characteristics for each contact including the age and sex of the contact, whether contact was physical (skin-to-skin contact), and where contact occurred (e.g. at home, work, while undertaking leisure activities, etc). Participants are instructed to report contacts individually, but are also given the opportunity to report aggregated estimates of contacts by age group and setting in case they did not list all contacts individually. Further details have been published elsewhere[1,2]. The contact survey is based on the POLYMOD contact survey[3]. 

We calculated and plotted the crude mean number of contacts by setting, duration, and participant to contact age groups. We used the settings home, work and school (including all educational establishments, including childcare, nurseries and universities and colleges), and “other”  (mostly leisure and social contacts, but includes shopping), and report . We look at the mean contacts by age and survey wave. The mean number of contacts is influenced by a few individuals who report very high numbers of contacts (often in a work context). We show means for all contacts and means number of contacts after truncating the maximum number of contacts recorded at 50 per individual per day.

We calculated the mean contacts for the contact matrices by using the socialmixr R package [4], with `r matrix_boots_n` bootstrapped samples. We used the World Population Prospect data from 2015 for country specific population estimates  by age and gender, which is the latest available data in the socialmixr package. We constructed age-stratified contact matrices for nine age-groups (0-4, 5-11, 12-17, 18-29, 30-39, 40-49, 50-59, 60-69, and 70+). For contacts, we do not have exact ages and therefore sampled from the reported age-group.

 <br/>

### Timeline

The CoMix survey in `r country_name_` has had `r length(unique(part$wave))` waves of data collection covering from the period `r format(min(part$survey_date), "%d of %B %Y")` to `r format(max(part$survey_date), "%d of %B %Y")`. Figure 1 shows survey response by date.

```{r timetable, fig.cap="Table 1: Timeline of survey rounds"}

timetable <- part %>% group_by(wave) %>% 
  summarize(min_date = format(min(survey_date), "%d %b %y"), 
            max_date = format(max(survey_date), "%d %b %y"), 
            participants = n()) %>% 
  ungroup()

count_contacts <- contacts %>% count(wave, name = "contacts")

timetable <- left_join(timetable, count_contacts)

names(timetable) <- c("Wave","Start date","End date", "Participants", "Contacts")

kable(t(timetable)) %>% 
  kable_styling(full_width = F, position = "left")

```
<strong>Table 1. Survey wave summary.</strong> Survey wave start and end dates, number of participants, and number of contacts.

<br/>

<strong>Figure 1: Survey responses by date.</strong>

```{r response_day_participants, fig.height=4, fig.width=6}

obs_per_date <- part %>% 
  count(wave, survey_date) %>%
  mutate(survey_date)

ggplot(obs_per_date) +
  geom_col(aes(y = n, x = survey_date)) +
  facet_grid(. ~ wave, scales = "free_x", space = "free_x") +
  scale_x_date(breaks = "2 day", 
               expand = expansion(0), 
               date_labels = "%d %b %y") +
  labs(y = "Number of participants", x = "Date of contact") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.3)) 



```


<br/>

### Participant demographics

<br/>

```{r participant_table, echo=FALSE}

part_summary_age <- part %>%
  count(wave, part_age_group) %>%
  group_by(wave) %>%
  mutate(prop = prop.table(n), 3) %>%
  mutate(display = paste(n, " (", format_n(prop * 100), "%)", sep = ""))

part_summary_gender <- part %>%
  count(wave, part_gender) %>%
  group_by(wave) %>%
  mutate(prop = round(prop.table(n), 3)) %>%
  mutate(display = paste(n, " (", format_n(prop * 100), "%)", sep = ""))

part_summary_hh_size <- part %>% 
  count(wave, hh_size_group) %>%
  group_by(wave) %>%
  mutate(prop = round(prop.table(n), 3)) %>%
  mutate(display = paste(n, " (", format_n(prop * 100), "%)", sep = ""))

# part_summary_pop_dens <- part %>%
#   count(wave, popul) %>%
#   group_by(wave) %>%
#   mutate(prop = round(prop.table(n), 3)) %>%
#   mutate(display = paste(n, " (", (prop * 100), "%)", sep = ""))


part_summary_display_age <- part_summary_age %>% 
  pivot_wider(id_cols = "part_age_group", names_from = "wave", values_from = "display", names_prefix = "Wave ") %>% 
  rename(Group = part_age_group) %>%
  mutate(Category = "Age")

part_summary_display_gender <- part_summary_gender %>%
  pivot_wider(id_cols = "part_gender", names_from = "wave", values_from = "display", names_prefix = "Wave ") %>%
  rename(Group = part_gender) %>%
  mutate(Category = "Gender",
         Group = case_when(
           Group == "female" ~ "Female",
           Group == "male" ~ "Male",
           is.na(Group) ~ "Other or Missing"
         ))


part_summary_display_hh_size <- part_summary_hh_size %>% 
  pivot_wider(id_cols = "hh_size_group", names_from = "wave", values_from = "display", names_prefix = "Wave ") %>% 
  rename(Group = hh_size_group) %>%
  mutate(Category = "Household size")


all_summary <- part %>%
  count(wave) %>% mutate(Category = "All") %>%
  rename(display = n) %>%
  pivot_wider(id_cols = "Category", names_from = "wave", values_from = "display", names_prefix = "Wave ")

full_summary <- rbindlist(list(
  all_summary,
  part_summary_display_age,
  part_summary_display_gender,
  part_summary_display_hh_size), fill  = TRUE
) %>% relocate(Group, .after = Category)

full_summary[is.na(Group)]$Group <- ""

kable(full_summary) %>% 
  kable_styling(full_width = F, position = "left") %>%
  collapse_rows(columns = 1, valign = "top")

# FOR WORD TABLES
# theme_vanilla(flextable(full_summary))
```

<strong>Table 2. Participant demographics by wave for age, gender, and household size.</strong>

<br/>

### Contact characteristics

<br/>

#### Contact setting

<br/>

<strong>Figure 2. Proportion of contacts by setting and wave.</strong> A) All contacts (both individually-reported and reported in aggregated contact questions); B) individually-reported contacts only.

```{r contact_setting, echo = FALSE, fig.width = 7, fig.height = 4}

setting_all <- ggplot(
  contacts, 
  aes(y = factor(wave), fill = factor(cnt_setting))) + 
  geom_bar(position="fill", stat="count") +
  ylab("Wave") +
  xlab("Proportion") +
  labs(fill = "Contact setting") +
  coord_flip() +
  # scale_fill_manual(values = rev(fresh_pallette[c(2:6,8)]), guide = guide_legend(reverse = TRUE)) +
  ggtitle("A. All contacts") +
  theme_bw() +
  theme(plot.title = element_text(size=12)) 

# total_time_all


setting_individual <- ggplot(
  contacts %>% filter(cnt_mass == "individual"), 
  aes(y = factor(wave), fill = factor(cnt_setting))) + 
  geom_bar(position="fill", stat="count") +
  ylab("Wave") +
  xlab("Proportion") +
  labs(fill = "Contact setting") +
  coord_flip() +
  ggtitle("B. Individually-reported contacts") +
  theme_bw() +
  theme(plot.title = element_text(size=12))

# total_time_non_household 

comb_setting <- (setting_all + setting_individual) + plot_layout(guides = "collect") 
comb_setting

cnt_summary_setting <- contacts %>%
  count(wave, cnt_setting) %>%
  group_by(wave) %>%
  mutate(prop = round(prop.table(n), 3)) %>%
  mutate(display = paste(n, " (", format_n(prop * 100), "%)", sep = "")) %>%
  pivot_wider(id_cols = "cnt_setting", names_from = "wave", values_from = "display", names_prefix = "Wave ")  %>%
  rename("Group" = cnt_setting) %>%
  mutate(Category = "Contact setting") %>%
  relocate(Category, .before = Group)

# kable(cnt_summary_setting)  %>% kable_styling(full_width = F, position = "left")

```

<br/>

#### Contact duration

<br/>

<strong>Figure 3. Proportion of contacts by duration of contact and wave.</strong> A) All individually-reported contacts; B) individually-reported contacts, excluding the participant's household members.

```{r contact_duration, echo = FALSE, fig.width = 7, fig.height = 4}

total_time_all <- ggplot(
  contacts %>% filter(cnt_mass == "individual"), 
  aes(y = factor(wave), fill = factor(cnt_total_time))) + 
  geom_bar(position="fill", stat="count") +
  ylab("Wave") +
  xlab("Proportion") +
  labs(fill = "Contact time") +
  coord_flip() +
  # scale_fill_manual(values = rev(fresh_pallette[c(2:6,8)]), guide = guide_legend(reverse = TRUE)) +
  ggtitle("A. Individual contacts") +
  theme_bw() +
  theme(plot.title = element_text(size=12))

# total_time_all


total_time_non_household <- ggplot(
  contacts %>% filter(cnt_mass == "individual" & cnt_household == 0), 
  aes(y = factor(wave), fill = factor(cnt_total_time))) + 
  geom_bar(position="fill", stat="count") +
  ylab("Wave") +
  xlab("Proportion") +
  labs(fill = "Contact time") +
  coord_flip() +
  # scale_fill_manual(values = rev(fresh_pallette[c(2:6,8)]), guide = guide_legend(reverse = TRUE)) +
  ggtitle("B. Non-household contacts") +
  theme_bw() +
  theme(plot.title = element_text(size=12))

# total_time_non_household 

comb_total_time <- (total_time_all + total_time_non_household) + plot_layout(guides = "collect")

comb_total_time 


cnt_summary_duration <- contacts %>%
  filter(cnt_mass == "individual") %>%
  count(wave, cnt_total_time) %>%
  group_by(wave) %>%
  mutate(prop = round(prop.table(n), 3)) %>%
  mutate(display = paste(n, " (", format_n(prop * 100), "%)", sep = "")) %>%
  pivot_wider(id_cols = "cnt_total_time", names_from = "wave", values_from = "display", names_prefix = "Wave ")  %>%
  rename("Group" = cnt_total_time) %>%
  mutate(Category = "Contact time") %>%
  relocate(Category, .before = Group)
# kable(cnt_summary_duration)  %>% kable_styling(full_width = F, position = "left")

```

<br/>

```{r cnt_summary_table, echo = FALSE}
cnt_summary_table <- rbindlist(list(cnt_summary_setting, cnt_summary_duration))

kable(cnt_summary_table) %>% 
  kable_styling(full_width = F, position = "left") %>%
  collapse_rows(columns = 1, valign = "top")
```

<strong>Table 3. Contacts by setting and duration of contact and wave.</strong> Number and percentage of contacts by category for all contacts (individually-reported and reported in aggregated contact questions).

<br/>

#### Contact means

<br/>

<strong>Figure 4. Crude mean contacts by participant age group and wave.</strong>   Reported by all contacts and contacts truncated to 50 per participant per day.

```{r contact_means_plot, echo=FALSE, message = FALSE, warning = FALSE}

all_mean <- contacts %>% 
  count(wave, part_id) %>%
  group_by(wave) %>%
  summarise("Mean contacts" = mean(n)) %>%
  mutate(Contacts = "All contacts", "Participant age" = "All") 
 

trunc_mean <- trunc_contacts %>% 
  count(wave, part_id) %>%
  group_by(wave) %>%
  summarise("Mean contacts" = mean(n)) %>%
   mutate(Contacts = "Truncated to 50 contacts per participant", "Participant age" = "All") 



all_mean_age <- contacts %>% 
  count(wave, part_id, part_age_group) %>%
  group_by(wave, part_age_group) %>%
  summarise("Mean contacts" = mean(n)) %>%
  mutate(Contacts = "All contacts") %>% 
  rename("Participant age" = part_age_group)

trunc_mean_age <- trunc_contacts %>% 
  count(wave, part_id, part_age_group) %>%
  group_by(wave, part_age_group) %>%
  summarise("Mean contacts" = mean(n)) %>%
  mutate(Contacts = "Truncated to 50 contacts/participant") %>% 
  rename("Participant age" = part_age_group) 

contact_means <- rbindlist(list(all_mean, trunc_mean, all_mean_age, trunc_mean_age), use.names = T) %>%
  rename(Wave = wave) %>%
  mutate("Mean contacts"= round(`Mean contacts`, 2)) %>%
  select("Wave", "Contacts", "Participant age", "Mean contacts") 


contact_means_table <- contact_means %>%
  pivot_wider(id_cols = c("Contacts", "Participant age"), 
              names_from = "Wave", 
              values_from = "Mean contacts", 
              names_prefix = "Wave ")

contact_means_ages <- contact_means %>% filter(`Participant age` != "All") %>%
  mutate(Wave = paste("Wave", Wave))

ggplot(contact_means_ages, aes(x = `Participant age`, y = `Mean contacts`,
       fill = `Participant age`)) +
  geom_col(position = "dodge") +
  xlab("Partcipant age") +
  facet_grid(rows = vars(Contacts), cols = vars(factor(Wave))) +
  theme_bw() +
  ylab("Mean number of contacts")
```

<br/>

```{r contact_means_table}
kable(contact_means_table) %>%
  kable_styling(full_width = F, position = "left") %>%
  collapse_rows(columns = 1, valign = "top")
```
<strong>Table 4. Crude mean contacts by participant age group for each wave.</strong>

<br/>

### Contact Matrices

<br/>

#### All contacts

<br/>

<strong>Figure 5. Contact matrices by wave.</strong> Contacts truncated to 50 per participant per day, adjusted for day of week.

```{r contact_matrices, echo=FALSE}
# Plot generated in `r/socialmixr_matrices.R`
source(file.path(here::here(), "r", "socialmixr_matrices.R"))

cm_plot_all
```

<br/>

<strong>Figure 6. Adjusted contact means by participant age group.</strong> Contacts truncated to 50 per participant per day, adjusted for day of week.

```{r adjusted_mean_figure, fig.height = 3, fig.width = 9}

ggplot(adj_mean_contacts_all, aes(y = mean_contacts, x = participant_age,
                              fill = participant_age)) +
  geom_col() +
  facet_grid(cols = vars(wave)) + 
  xlab("Participant age") +
  ylab("Mean contacts") +
  labs(fill = "Participant age") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.3))  

  
```

<br/>

<strong>Table 5. Adjusted contact means by participant age group.</strong> Contacts truncated to 50 per participant per day, adjusted for day of week.

```{r adjusted_mean_table_all}
kable(adj_mean_contacts_table_all, digits = 2) %>% kable_styling(full_width = F, position = "left")
```


<br/>


#### Adult contacts

<br/>

<strong>Figure 7. Symmetric adult participant to adult contact matrices by wave.</strong> Contacts truncated to 50 per participant per day, adjusted for day of week and country population by age using the World Population Prospect population data.

```{r contact_matrices_adult, echo=FALSE}
# Plot generated in `r/socialmixr_matrices.R`

cm_plot_adult
```

<br/>


<strong>Figure 8. Adult participant to adult contact means by wave.</strong> Contact means as calculated from symmetric, adult participant to adult contact symmetric matrices. Contacts truncated to 50 per participant per day, adjusted for day of week and country population by age using the World Population Prospect population data.

```{r adjusted_mean_figure_adult, fig.height = 3, fig.width = 9}

ggplot(adj_mean_contacts_adult, aes(y = mean_contacts, x = participant_age,
                              fill = participant_age)) +
  geom_col() +
  facet_grid(cols = vars(wave)) + 
  xlab("Participant age") +
  ylab("Mean contacts") +
  labs(fill = "Participant age") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.3))  


# ggthemr::ggthemr("grape")
# ggplot(adj_mean_contacts_adult, 
#        aes(y = mean_contacts, 
#            x = wave,
#            group = participant_age, 
#            color = participant_age)) +
#   geom_point() +
#   geom_line() +
#   expand_limits(y = 0) +
#   facet_wrap(vars(participant_age)) +
#   xlab("Wave") +
#   ylab("Mean contacts") +
#   labs(color = "Participant age") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.3))  
  
```

<br/>

<strong>Table 6. Adult participant to adult contact means by wave.</strong> Contact means as calculated from symmetric, adult particpant to adult contact symmetric matrices. Contacts truncated to 50 per participant per day, adjusted for day of week and country population by age using the World Population Prospect population data.

```{r adjusted_mean_table_adult}
kable(adj_mean_contacts_table_adult, digits = 2) %>% kable_styling(full_width = F, position = "left")
```


<br/>

#### References

1.  Jarvis CI, Van Zandvoort K, Gimma A, Prem K, CMMID COVID-19 working group, Klepac P, et al. Quantifying the impact of physical distance measures on the transmission of COVID-19 in the UK. BMC Med. 2020;18: 124.

2.  Coletti P, Wambua J, Gimma A, Willem L, Vercruysse S, Vanhoutte B, et al. CoMix: comparing mixing patterns in the Belgian population during and after lockdown. Sci Rep. 2020 Dec;10(1):21885. 

3. 	Mossong J, Hens N, Jit M, Beutels P, Auranen K, Mikolajczyk R, et al. Social contacts and mixing patterns relevant to the spread of infectious diseases. PLoS Med. 2008;5: e74. 

4. Sebastian Funk (2020). socialmixr: Social Mixing Matrices for Infectious Disease Modelling. R package version 0.1.7.
